%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{my_resume} % Use the custom resume.cls style

\usepackage[left=1in,top=0.4in,right=0.8in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jordan Hong} % Your name
\address{jordan.hong@mail.utoronto.ca} % Your phone number and email

\begin{document}

    %----------------------------------------------------------------------------------------
    %    EDUCATION SECTION
    %----------------------------------------------------------------------------------------

    \begin{rSection}{Education}
        2\textsuperscript{nd} year Engineering Science, University of Toronto    \hfill{ B.A.Sc. expected in 2023}
    \end{rSection}





    %----------------------------------------------------------------------------------------
    %    PROJECTS SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Projects and Design Work}    
        
        {\bf Autonomous Car Charger Deliver Robot} \hfill{2020}
             \begin{itemize}
                \setlength\itemsep{-0.5em}
                \item blah
            \end{itemize} 

        {\bf StayEnglightened, MakeUofT} \hfill{2020}
            \begin{itemize}
                \setlength\itemsep{-0.5em}
                \item blah
            \end{itemize} 
        
        {\bf Automated Dough Fermentation Tester} \hfill{2019}
        \begin{itemize}
            \setlength\itemsep{-0.5em}
            \item Developed device prototype for dough fermentation tester using computer vision(OpenCV) and image processing as part of Praxis group project. Personal contribution entailed embedded system design with Raspberry Pi module. 
            \item Represented University of Toronto Engineering Science students to showcase in the \emph{2019 International Engineering Science Consortium}. 
        \end{itemize}
            
        {\bf Android Productivity Application-Finite} \hfill{2018-2019} 
        \begin{itemize}
            \setlength\itemsep{-0.5em}
            \item Collaborated with a partner to develop a time-productivity Android application. Personal work entailed backend text and image data storage. (Launched on Google Play store December 2018).
            
        \end{itemize}


    \end{rSection}


    %----------------------------------------------------------------------------------------
    %    RESEARCH SECTION
    %----------------------------------------------------------------------------------------


    \begin{rSection}{Research Experience}
    
        {\bf Advanced Composite Characterization Lab}, University of Toronto     \hfill{2019-05 - present}\\
        Undergraduate Researcher with Prof. Ning Yan and Postdoctoral Fellow Nicolas Tanguy\\
        Topic: Polyaniline-Nanocellulose-based green films for ammonia sensing applications. 
        \begin{itemize}
            \setlength\itemsep{-0.5em}
            \item Developed and optimized chamber and electrical testing environment for monitoring chemoresistance of green semiconductive films. 
            \item Investigated compositions of different nanomateirals to optimize sensing performance of nanocellulose-based films.
            \item Developed Python script to automate data association and perform analysis.
        \end{itemize}


    \end{rSection}

        
    %----------------------------------------------------------------------------------------
    %    SKILLS SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Skills}
        {\bf Programming: } Python, C, Java, Javascript, MATLAB\\
        {\bf Embedded Systems: } Verilog, Raspberry Pi, Arduino \\
        {\bf Design: } HTML, Processing3, Android Studio\\ 
        {\bf Developer tools: } Unix, Vim, Git
    \end{rSection}



    %----------------------------------------------------------------------------------------
    %    AWARDS SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Awards}
        {\bf Faculty of Engineering Dean's Honour List}, University of Toronto \hfill{2018, 2019, 2020} \\
        {\bf Faculty of Engineering Admission Scholarship}, University of Toronto \hfill{2018-09} \\
        {\bf York Mills CI Gold Award}, York Mills Collegiate Institute \hfill{2018-06}\\ 
        {\bf Award of Excellence-International Olympiad Research}, Taiwan \hfill{2016-08} \\
        {\bf Taipei Mayor Award}, Taipei city government \hfill{2015-06}
    \end{rSection}



    %----------------------------------------------------------------------------------------
    %        OTHER SERVICES SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Extracurriculars}
        {\bf University of Toronto Robotics Association} \hfill{2019-present}    \\        
        SUMO Design Team Member- Electrical Design\\
        {\bf Canadian Chinese Orchestra}, Markham  \hfill{2017-present}\\ 
        Erhu \& Zhonghu \\
        {\bf Newcomers Association}, York Mills Collegiate Institute \hfill{2016-2018}\\
        Vice Chair
    \end{rSection}



\end{document}
