%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{my_resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.4in]{geometry} % Document margins
%\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
%\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jordan Hong} % Your name
\address{jordan.hong@mail.utoronto.ca \\ https://github.com/jordanhong} % Your phone number and email
\begin{document}



\begin{minipage}[t]{0.3\textwidth}
    \begin{rSection}{Education}
        \textmd{BASc, University of Toronto}\\ 
        {\small 2\textsuperscript{nd} year Engineering Science\\
        Electrical \& Computer Option \vskip 5pt
        }
        \textmd{York Mills Collegiate Institute} \vskip 5pt 
                
        \textmd{Affiliated Senior High School of National Taiwan Normal University} 
   
    \end{rSection}
    \begin{rSection}{Skills}
        \textbf{Programming }\\ 
        Python, C, Java, Javascript, MATLAB, Verilog\\
        \textbf{Libraries}\\
        NumPy, Matplotlib, OpenCV\\
        \textbf{Embedded Systems } \\
        Raspberry Pi, Arduino \\
        \textbf{Design }\\ 
        HTML, Processing3, Android Studio\\ 
        \textbf{Developer tools}\\
         Bash, Zsh, Vim, Git\\
        \textbf{OS}\\
        Linux, macOS, Windows\\
        \textbf{Typesetting}\\
        \LaTeX, Markdown\\
        \textbf{Languages}\\
        Mandarin Chinese, English\\
    \end{rSection}
    

    \begin{rSection}{Coursework}
        \textbf{ECE/Computer Science}\\
        Algorithms \& Data Structures\\
        Digital and Computer System \\
        Electric Circuits\\
        Electromagnetism\\
        \textbf{Physics}\\
        Classical Mechanics\\
        Modern Physics\\
        Quantum Physics\\
        \textbf{Mathematics}\\
        Calculus\\
        Differential Equations\\
        Vector Calculus\\ 
        Linear Algebra\\   
    \end{rSection}

         
\end{minipage}
\hspace{0.04\textwidth}
\begin{minipage}[t]{0.66\textwidth} 




    %----------------------------------------------------------------------------------------
    %    PROJECTS SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Projects and Design Work}    
 
        \textbf{Autonomous Car Charger Deliver Robot} \hfill{2020}
        \begin{itemize}
            \item Electrical design: integrated peripherals with the Raspberry Pi. Implemented python to control motors and camera. 
            \item Contributed to high level software programming with OpenCV and image processing  to detect charging port. 
        \end{itemize}

        \vspace{5pt} 
        \textbf{StayEnglightened, MakeUofT} \hfill{2020}\\
       Developed a IoT-based smart lighting system for student study areas.
            \begin{itemize}
                \item Integrated the peripherals on the Qualcomm DragonBoard 410C with linux-based Debian environment. Implemented serial communication between Python ennvironment and on-board Arduino processor.
            \end{itemize} 
        
        \vspace{5pt} 
        \textbf{Automated Dough Fermentation Tester} \hfill{2019}
        \begin{itemize}
           %\setlength\parskip{1em}
            \item Developed device prototype for dough fermentation tester using computer vision(OpenCV) and image processing. 
            \item Personal contribution entailed embedded system design with Raspberry Pi module. 
        \end{itemize}
            
        \vspace{5pt} 
        \textbf{Android Productivity Application-Finite} \hfill{2018-2019} 
        \begin{itemize}
           % \setlength\itemsep{-0.5em}
            \item Collaborated with a partner to develop a time-productivity Android application. Personal work entailed backend text and image data storage. (Launched on Google Play store December 2018).
            
        \end{itemize}

    \vspace{5pt}
    \end{rSection}


    %----------------------------------------------------------------------------------------
    %    RESEARCH SECTION
    %----------------------------------------------------------------------------------------


    \begin{rSection}{Research Experience}
    
        \textbf{Advanced Composite Characterization Lab}     \hfill{2019}\\
        Summer Undergraduate Researcher\\
        Topic: Polyaniline-Nanocellulose-based green films for ammonia sensing applications. 
        \begin{itemize}
            %\setlength\itemsep{-0.5em}
            \item Developed and optimized chamber and electrical testing environment for monitoring chemoresistance of green semiconductive films. 
            \item Investigated compositions of different nanomateirals to optimize sensing performance of nanocellulose-based films.
            \item Developed Python script to automate data association and perform analysis.
        \end{itemize}


    \end{rSection}

        

    %----------------------------------------------------------------------------------------
    %    AWARDS SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Awards}
        Faculty of Engineering Dean's Honour List \hfill{2018, 2019, 2020} \\
        Faculty of Engineering Admission Scholarship\hfill{2018} \\
        York Mills Collegiate Institute Gold Award  \hfill{2018}\\ 
        International Olympiad Research, Taiwan \hfill{2016} \\
        Taipei Mayor Award \hfill{2015}
    \end{rSection}



    %----------------------------------------------------------------------------------------
    %        OTHER SERVICES SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Extracurriculars}
        \textbf{University of Toronto Robotics Association} \hfill{2019}    \\        
        SUMO Design Team Member- Electrical Design\\
        \textbf{Canadian Chinese Orchestra}, Markham  \hfill{2017}\\ 
        Erhu \& Zhonghu \\
        \textbf{Newcomers Association}, York Mills Collegiate Institute \hfill{2016-2018}\\
        Vice Chair
    \end{rSection}


\end{minipage}
\end{document}
