%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[hidelinks]{my_resume} % Use the custom resume.cls style
\usepackage{hyperref}
\usepackage[left=0.6in,top=0.5in,right=0.6in,bottom=0.4in]{geometry} % Document margins
\name{Jordan Hong} % Your name
\email{jordan.hong@mail.utoronto.ca}
\address{linkedin.com/in/jordan-hong}
\address{github.com/jordanhong}
\begin{document}
    \begin{minipage}[t]{0.3\textwidth}
        \begin{rSection}{Education}
        \vspace{5pt}
            BASc, University of Toronto \\
            3\textsuperscript{rd} year Engineering Science
            \medskip
            \begin{itemize}
                \item ECE Division 
                \item cGPA: 3.73
            \end{itemize}
        \end{rSection}

        \vspace{10pt} 
        \begin{rSection}{Skills}
        \vspace{5pt}
            \textbf{HDL and FPGA}
            \begin{itemize}
                \item   Verilog
                \item   ModelSim, Quartus, Vivado
            \end{itemize}
            
            \textbf{Circuit Design \& Simulation}
            \begin{itemize}
                \item   Altium
                \item   LTSpice
            \end{itemize}
            \textbf{Embedded Systems }
            \begin{itemize}
                \item Raspberry Pi, Arduino 
            \end{itemize}
        \vspace{5pt}
            \textbf{Software}
            \begin{itemize}
                \item Python, C, MATLAB
            \end{itemize}
            \textbf{Developer tools}
            \begin{itemize}
                \item Vim, Git, Perl, Bash
            \end{itemize}
            \textbf{OS}
            \begin{itemize}
                \item Linux, macOS, Windows
            \end{itemize}
            \textbf{Languages}
            \begin{itemize}
                \item Mandarin Chinese, English
            \end{itemize}
        \end{rSection}
       
        \bigskip
        \begin{rSection}{Course work}
            \medskip
            \textbf{ECE/Computer Science}
            \begin{itemize}
                \item Algorithms \& \\ Data Structures
                \item Digital \& Computer System 
                \item Electric Circuits
                \item Electromagnetism 
            \end{itemize}
            \smallskip
            3\textsuperscript{rd} year courses:
            \begin{itemize}
                \item Electronic Circuits
                \item Semiconductor Electronics
            \end{itemize}

            \medskip
            \textbf{Physics}
            \begin{itemize}
                \item Classical Mechanics
                \item Modern Physics
                \item Quantum Physics
                \item Thermal Physics
            \end{itemize}
            \medskip
            \textbf{Mathematics}
            \begin{itemize}
                \item Calculus
                \item Differential Equations
                \item Vector Calculus
                \item Linear Algebra
            \end{itemize}
        \end{rSection}

             
    \end{minipage}
    \hspace{0.04\textwidth}
    \begin{minipage}[t]{0.66\textwidth} 




    %----------------------------------------------------------------------------------------
    %    PROJECTS SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Engineering Work}
        \vspace{5pt}
        \href{https://www.mpi-halle.mpg.de/NINT}{\textbf{Max Planck Institute (NINT department)}}, Germany    \hfill{2020}\\
        \emph{FPGA Engineer (Summer Intern) with Dr. Joyce Poon}
        \vspace{5pt}
        \begin{itemize}
            \item Implemented PWM-generating circuit for thermo-optic MZI silicon photonic switches on FPGA using Verilog. Realized high timing \mbox{resolution} by utilizing Vernier effect.
            \item C driver to interface with USB-I2C converter and control PWM LED driver
            \item GPU DMA Framework for FPGA-hosted accelerated neural \mbox{networks} and image processing. Current work involves Intel (Altera) PCIe core with Avalon interface and Direct Memory Access. 
        \end{itemize}

    \end{rSection}
        \vspace{5pt} 
    \begin{rSection}{Projects}    
        \vspace{5pt} 
        \textbf{LumineSense}, University of Toronto based venture   \hfill{2020} \\
        \emph{Co-founder}
        \begin{itemize}
            \item Smart UV lamp for surface disinfection in response to COVID-19.
            \item Software division: Raspberry Pi programming, sensors integration, and system control using Python. 
        \end{itemize}

        \vspace{5pt} 
        \textbf{Autonomous Car Charging Robot} \hfill{2020}\\
        \emph{2\textsuperscript{nd} year robotics course project}
        \begin{itemize}
            \item Designed boost converter with LTSpice for electric motor.
            \item System integration (camera, electric motor, microswitches) with the Raspberry Pi using Python. 
            \item PCB design (wiring, soldering, breadboard prototype).  
        \end{itemize}
    \end{rSection}

        \vspace{5pt} 

    %----------------------------------------------------------------------------------------
    %    RESEARCH SECTION
    %----------------------------------------------------------------------------------------


    \begin{rSection}{Research Experience}
        \vspace{5pt} 
    
        \href{https://ningyanlab.com/}{\textbf{Yan Lab, University of Toronto}}     \hfill{2019}\\
        \emph{Summer Undergraduate Researcher with Prof. Ning Yan (Chem Eng)} \\
        Topic: Polyaniline-Nanocellulose-based green films for chemical sensors. 
        \begin{itemize}
            \item Designed chamber for monitoring chemoresistance of green semiconductive films and investigated compositions of nanomaterials.
            \item Data analysis using Python. 
        \end{itemize}
    \end{rSection}
\vspace{5pt}

        

    %----------------------------------------------------------------------------------------
    %    AWARDS SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Awards}
        MITACS Globalink Research Award [declined]             \hfill{2020}\\
        Engineering Science Research Fellowship (ESROP) [declined] \hfill{2020}\\
        Faculty of Engineering Dean's Honour List \hfill{2018-2020} \\
        Faculty of Engineering Admission Scholarship\hfill{2018} \\
        International Olympiad Research, Taiwan \hfill{2016} \\
        Tapei Mayor Academic Award, Taiwan      \hfill{2015} 
    \end{rSection}



    %----------------------------------------------------------------------------------------
    %        OTHER SERVICES SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Extracurriculars}
        \textbf{University of Toronto Robotics Association} \hfill{2019-2020}   
        \begin{itemize}
            \item SUMO Design Team Member- Electrical Design
        \end{itemize}
        \textbf{Canadian Chinese Orchestra}, Markham        \hfill{2018-2019}
        \begin{itemize}
            \item Member (Erhu, Zhonghu)
        \end{itemize}
    \end{rSection}
\end{minipage}

\end{document}
